### 2009-02-23 doc/ws-programming-tutorial/doc/tex_introduction/introduction.tex
I wrote more in for the time service and try to push the other services further

Servers provide access to a single service or a set of services. For ARC, there is one service, named Hosting Environment Demon (hed), more special than other services: hed organises the assignment of other services on the same server to the network. But this does not break the concept, it is only a commodity. If services are not busy reacting to a client's request, then they are waiting. The task of servers can be subdivided into:
\begin{itemize}
 \item Wait for client request
 \item Receive the request
 \item Perform the desired service
 \item Create a response for the client
 \item Send response to the client
 \item Wait for next client request
\end{itemize}
While the server waits passively for a request, the client acts actively:
\begin{itemize}
 \item Create a request
 \item Transmit the request to the server which provides the desired service.
 \item Receive the response from the server.
 \end{itemize}
\forcelinebreak

In general, the implementation of a client is easier that the implementation of the server. 
ARC is designed as a middleware which encapsulates typical challenges of server-client infrastructures (security, exception handling, extensibility) and abstracts from underlying architecture (heterogeneity of computers, computer location, protocols).
The core of KnowArc is the prior mentioned HED (Hosting Environment Daemon). To the administrator HED hed is mostly visible as the single binary that is started and by the configure file that describes the other services that shall be prepared by HED. Conceptionally, the HED determines how services shall be organised both as a principle, and for any given ARC-run server, HED determines the very explicit presence or absence of a service at a particular address. Its many configurable layers are described later in this tutorial. 
%
At the time of writing, the endpoint of the HED will be a SOAP based webservice.
SOAP is a long established XML-based standard for web service communication.
ARC abstracts from this format, but nevertheless it is useful to be aware of
the underlying message transport mechanism.

@@

The source code of the examples given in this tutorial are available in the subdirectory \textit{src}\footnote{If this was not shipped with the document you are reading, then please inspect http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/doc/ws-programming-tutorial}.

@@

The HED which was already mentioned in the section above as an essential part of the ARC middleware. It provides hosting of various services at application level, as well as a number of modules~\cite{QIANG_2005}. Figure~\ref{fig:HED_internal} illustrates a typical setup of a server sided HED. The HED consists of a few compononents called Message Chain Components (MCC) which are ordered within a layered structure and several \textcolor{urgent}{modules} which shall aid the programmer to simplify the development of the Web Services (Config, Loader, Logging, XMLNode).
%
\begin{figure}
	\centering
	\includegraphics[width=14cm]{tex_introduction/HED.pdf}
	\mycaption{Example of HED structure with an Arex service and a file service.\task{ Replace image by an easier one!} }{\task{Write more stuff}\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}}
\label{fig:HED_internal}
\end{figure}
The MCCs are passing the incoming and outgoing messages to the upper or the respective lower layer.
% AUFZÄHLUNG???
The lowest layer has to be a transport protocol like TCP which enables the transmission between the two applications, the client and the server. (The Internet Protocol (IP) beneath the TCP layer enables a transmission between two computers. IP is needed but not part of the HED.) TCP is well suited for the application because it provides a reliable and ordered delivery of a byte stream which is important to ensure security and a requirement for the usage of HTTP.
The TCP layer is followed by the Hypertext Transfer Protocol (HTTP). 
In case a security layer is desired, the TLS (Transport Layer Security formerly known as SSL, Secure Sockets Layer) can be inserted between the two layers TCP and HTTP.
The HTTP provides the client server architecture. It is stateless but offers several extensions for requests, header information and status codes. Furthermore HTTP enables the usage of Uniform Resource Locators (URL) which is used by KnowArc to multiplex between different services. The multiplexing layer needs to be defined within the HED and is called Plexer. Depending on the path of the URL the Plexer passes messages to a defined SOAP service which again passes the message to the Web Service.\\

The structure of the HED can be configured freely by modifying the HED configuration file. A first impression how the HED can be configured shall be given in the following example which corresponds to the HED shown in figure~\ref{fig:HED_internal}. It uses the internal ARC Echo service.

\subsection{The Arcecho service}
\task{Maybe the word tag needs to be replaced by the word element...}
\task{Where is the xsd file for HED configuration files??}
The first example shall give a basic understanding in how to configure the HED. The task is to setup the ARC intern Echo Web Service which has to be done by invoking the \textit{arched} daemon with a fitting HED configuration file. Such a fitting HED configuration file is shown in Listing~\ref{lst:arched_arcecho_xml}. It is written in XML and its structure is based on the \textcolor{urgent}{??} schema.
\lstsetARCHEDXML\\
\begin{program}
\centering
\lstinputlisting
	[
	label=lst:arched_arcecho_xml,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/arched_arcecho.xml}
\end{program}
The first line of the XML file contains the XML declartion. Several attributes can be defined here but at least the XML version should be specified. \task{What is this ArcConfig for??} % configuration namespaces
The \textit{Server} tag, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as location of the Pid-file or the Log-file.
The \textit{ModuleManager} holds the path to the plugin libraries. Several paths may be defined here. Due to the fact that the first library fitting to the plugin name is loaded, the order is relevant. The path should be at least assigned to the ARC installation directory. % for the standard MCC are defined here
The next set of tags are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the name of the dynamic libraries within the path defined by the \textit{ModuleManager}.
Finally the chain of the components are declared initiate with the tag \textit{Chain}.
Each component inside the chain is represented by a tag called \textit{Component} which has at least a name attribute.
Its important that a plugin has been loaded which provides the functionality of it.
Depending on the component certain additional tags may be defined inside of it.
\task{Internet Protocol is required.}
The first component of the chain is the \textit{tcp.service}. As to be seen the port 60000 gets assigned for the server to listen to.
The stream which is received by this component is passed to the component defined by the \textit{next} tag.
In that case the will be passed to the component with the \textit{id} atrribute named \textit{http}. According to this manner the message will be passed to higher layers until it reaches the \textit{Plexer}  Depending on the path of the URL which was demanded by the HTTP the Plexer multiplexes the request to the right Web Service. The path is declared within the \textit{next} tag is a regular expression and leads to the service with the id named \textit{echo}. 
Which means that the service will be now reachable under URL \textit{http://localhost:60000/echo}.
This service finally will process the message and create a new message which will be returned all the way back to the TCP layer. The Echo Web Service itself is provided by the ARC package. Additional fix parameters can be passed by assigning tags which have to be known to the Web Service.
The tags \textit{echo:prefix} and \textit{echo:suffix} seen in this example are defining the characters which will enclose the echo  returned string.
\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}\\

To create the daemon corresponding to the defined HED configuration file ARC-1 provides the program \textit{arched}.
The manner of invokation can been seen in Listing~\ref{lst:arcecho_arched_invokation}.
\lstsetKSH
\begin{program}
\begin{lstlisting}[
label=lst:arcecho_arched_invokation,
caption={[Invokation of the Arched Daemon.]
         \textbf{Invokation of the Arched Daemon.\textcolor{white}{hmf}}}]

$ arched -c arcecho_no_ssl.xml && echo Daemon started || echo Daemon start failed
 Daemon started
$
\end{lstlisting}
\end{program}
% $ rm -f /var/log/arched.log
% $ tail -n100 -f /var/log/arched.log
%...
%$ killall arched
%
%
The command is followed by the parameter \textit{c} which assignes, that the next string contains the full path of configuration file.
Once the server is running, the client can be used as described in Listing~\ref{lst:arcecho_client_invokation}.
\lstsetKSH
\begin{program}
\begin{lstlisting}[
label=lst:arcecho_client_invokation,
caption={[Usage of the Arc echo client.]
         \textbf{Usage of the Arc echo client.\textcolor{white}{hmf}}}]
$ arcecho http://localhost:60000/Echo text
[ text ]
\end{lstlisting}
\end{program}
In this example the server and the client are running on the same computer. For debugging it is advisable to check the Log-file which was assigned inside the HED configuration file.\\

In the following chapters own Web Services will be developed. Starting with the simple Time Web Service.

>>>>

Servers provide access to a single service or a set of services. For ARC, there is one service, named Hosting Environment Demon (HED), more special than other services: HED organises the assignment of other services on the same server to the network. But this does not break the concept, it is only a commodity. If services are not busy reacting to a client's request, then they are waiting. The task of servers can be subdivided into:
\begin{itemize}
 \item Wait for client request
 \item Receive the request
 \item Perform the desired service
 \item Create a response for the client
 \item Send response to the client
 \item Wait for next client request
\end{itemize}
While the server waits passively for a request, the client acts actively:
\begin{itemize}
 \item Create a request
 \item Transmit the request to the server which provides the desired service.
 \item Receive the response from the server.
 \end{itemize}
\forcelinebreak

In general, the implementation of a client is easier \task{that} the implementation of the server. 
ARC is designed as a middleware which encapsulates typical challenges of server-client infrastructures (security, exception handling, extensibility) and abstracts from underlying architecture (heterogeneity of computers, computer location, protocols).
The core of Arc is the prior mentioned HED (Hosting Environment Daemon). To the administrator HED is mostly visible as the single binary that is started and configured by a file that describes services that shall be prepared by HED. Conceptionally, the HED determines how services shall be organised both as a principle, and for any given ARC-run server, HED determines the very explicit presence or absence of a service at a particular address. Its many configurable layers are described later in this tutorial. 
%
At the time of writing, the endpoint of the HED will be a SOAP based webservice.
SOAP is a long established XML-based standard for web service communication.
ARC abstracts from this format, but nevertheless it is useful to be aware of
the underlying message transport mechanism.

@@

The source code of the examples given in this tutorial are available in the subdirectory \textit{src}\footnote{If this was not shipped with the document you are reading, then please inspect\\ http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/doc/ws-programming-tutorial}.

@@

The HED which was already mentioned in the section above as an essential part of the ARC middleware provides hosting of various services at application level, as well as a number of modules. Figure~\ref{fig:HED_internal} illustrates a typical setup of a server sided HED. The HED consists of a few compononents called Message Chain Components (MCC) which are ordered within a layered structure and several \textcolor{urgent}{modules} which shall aid the programmer to simplify the development of the Web Services (Config, Loader, Logging, XMLNode).
%
\begin{figure}[htb]
	\centering
	\includegraphics[width=14cm]{tex_introduction/HED.pdf}
	\mycaption{Example of HED structure with an Arex service and a file service.\task{ Replace image by an easier one!} }{\task{Write more stuff}\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}}
\label{fig:HED_internal}
\end{figure}
The MCCs are passing the incoming and outgoing messages to the upper or the respective lower layer.
% AUFZÄHLUNG???
The lowest layer has to be a transport protocol like TCP which enables the transmission between the two applications, the client and the server. (The Internet Protocol (IP) beneath the TCP layer enables a transmission between two computers. IP is needed but not part of the HED.) TCP is well suited for the application because it provides a reliable and ordered delivery of a byte stream which is important to ensure security and a requirement for the usage of HTTP.
The TCP layer is followed by the Hypertext Transfer Protocol (HTTP). 
In case a security layer is desired, the TLS (Transport Layer Security formerly known as SSL, Secure Sockets Layer) can be inserted between the two layers TCP and HTTP.
The HTTP provides the client server architecture. It is stateless but offers several extensions for requests, header information and status codes. Furthermore HTTP enables the usage of Uniform Resource Locators (URL) which is used by Arc to multiplex between different services. The multiplexing layer can also be defined within the HED and is called Plexer. Depending on the path of the URL the Plexer passes messages to a defined SOAP service which again passes the message to the Web Service.\\

The structure of the HED can be configured freely by modifying the HED configuration file. A first impression how the HED can be configured shall be given in the following example which corresponds to the HED shown in figure~\ref{fig:HED_internal}. It uses the internal ARC echo service~\cite{QIANG_2005}.

\subsection{The arc echo service}

\task{Where is the xsd file for HED configuration files??}
The first example shall give a basic understanding in how to configure the HED. The task is to setup the ARC intern Echo Web Service which has to be done by invoking the \textit{arched} daemon with a fitting HED configuration file. Such a fitting HED configuration file is shown in Listing~\ref{lst:arched_arcecho_xml}. It is written in XML and its structure is based on the \textcolor{urgent}{??} schema.
\lstsetARCHEDXML\\

\lstinputlisting
	[
	label=lst:arched_arcecho_xml,float,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/arched_arcecho.xml}
The first line of the XML file contains the XML declartion. Several attributes can be defined here but at least the XML version should be specified. \task{What is this ArcConfig for??} % configuration namespaces
The \textit{Server} element, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as location of the Pid-file or the Log-file.
The \textit{ModuleManager} holds the path to the plugin libraries. Several paths may be defined here. Due to the fact that the first library fitting to the plugin name is loaded, the order is relevant. The path should be at least assigned to the ARC installation directory. % for the standard MCC are defined here
The next set of elements are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the name of the dynamic libraries within the path defined in the \textit{ModuleManager}.
Finally the chain of the components are declared within the element \textit{Chain}.
Each component inside the chain is represented by an element called \textit{Component} which has at least a name attribute.
Its important that a plugin has been loaded which provides the functionality of it.
Depending on the component certain additional elements may be defined inside of it.
\task{Internet Protocol is required.}
The first component of the chain is the \textit{tcp.service}. As to be seen the port 60000 is assigned to the server to listen to.
The stream which is received by this component is passed to the component defined by the \textit{next} tag.
In the present case it will be passed to the component with the \textit{id} atrribute named \textit{http}. According to this manner the message will be passed to higher layers until it reaches the \textit{Plexer}  Depending on the path of the URL which was demanded by the HTTP the Plexer multiplexes the request to the right Web Service. The path, declared within the \textit{next} element, corresponds to a regular expression and leads to the service with the id named \textit{echo}. 
Hence, the service will now be reachable under URL \textit{http://localhost:60000/echo}.
It will finally process the message and create a new message which will be returned all the way back to the TCP component. The Echo Web Service itself is provided by the ARC package. Additional fix parameters are passed by the elements \textit{prefix} and \textit{suffix}. They set the characters which will enclose the echoed string. %returned 
\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}\\

To create the daemon corresponding to the defined HED configuration file ARC provides the program called \textit{arched}.
The manner of invokation is to been seen in Listing~\ref{lst:arcecho_arched_invokation}.
\lstsetKSH
\begin{lstlisting}[
label=lst:arcecho_arched_invokation,float,
caption={[Invokation of the Arched Daemon.]
         \textbf{Invokation of the Arched Daemon.\textcolor{white}{hmf}}}]

$ arched -c arcecho_no_ssl.xml && echo Daemon started || echo Daemon start failed
 Daemon started
$
\end{lstlisting}

% $ rm -f /var/log/arched.log
% $ tail -n100 -f /var/log/arched.log
%...
%$ killall arched
%
%
The name of the program is followed by the parameter \textit{c} which assignes, that the next string contains the full path of configuration file. Once the server is running, the client can be used as described in Listing~\ref{lst:arcecho_client_invokation}.
\lstsetKSH
\begin{lstlisting}[
label=lst:arcecho_client_invokation,float,
caption={[Usage of the Arc echo client.]
         \textbf{Usage of the Arc echo client.\textcolor{white}{hmf}}}]
$ arcecho http://localhost:60000/Echo text
[ text ]
\end{lstlisting}

In this example the server and the client are running on the same computer so that the hostname \textit{localhost} can be utilized. 
For debugging it is advisable to check the Log-file which was assigned inside the HED configuration file.\\

In the following chapters own Web Services will be developed. The first one will be the simple Time Web Service.

### 2009-02-23 doc/ws-programming-tutorial/doc/tex_sec_echoservice/sec_echoservice.tex
I wrote more in for the time service and try to push the other services further

>>>>

POLICY STUFF:
copy the request out of the LOGGEr and use that to write your policy.xml
%/C=DE/ST=Germany/L=L\xFCbeck City/O=Instite of Neuro- and Bioinformatics/OU=Mitarbeiter

Deny-Overrides - this is default if no algorithm specified.
...
Administrator of service can configure Authorization SecHandler - arc.authz - for each MCC and Service
and define reasonable and meaningful policy. While defining policy the administrator must take into
account that the attributes defined in the policy should be already collected by previous components in a
chain. For instance, policy with AttributeId “http://www.nordugrid.org/schemas/policy-
arc/types/http/path” should not be configured inside SecHandler attached to MCCTLS.

### 2009-02-23 doc/ws-programming-tutorial/doc/tex_timeservice/timeservice.tex
I wrote more in for the time service and try to push the other services further

The first implementation of a Web Service which will be presented in this tutorial realises a simple time service.
In case the service receives a request, it will respond with a string containing the systemtime.
For simplicity the service will not parse the request but always return the current time.
In the following subsections the C++ implementation first the service and than the client will be developed.

@@

In Arc-1 the services are implementated as plugins such that they can easily be included by modifiying the HED configuration file as it was to be seen in Listing~\ref{lst:arched_arcecho_xml}.
The Listing~\ref{lst:time_arched_cpp}.shows the implementation of the time service plugin.
The proper class definition is defined in the corresponding header file which isn't shown here.
The key element for each plugin is the struct PluginDescriptor named PLUGINS\_TABLE\_NAME, see line\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin. 
Within the struct a unique plugin name, the type of the plugin, its version and the pointer to the function which returns the time service instance has to be defined.
The function which returns the pointer to an instance of the service needs to have the PluginArgument as a parameter. 
The actual Time Web Service is implemented within the namespace ArcService. The constructor can be found in line~\ref{lst_code:time_cpp_constructor}, the deconstructor in line~\ref{lst_code:time_cpp_deconstructor} and the method required by the inherited class \textit{Service} file in line~\ref{lst_code:time_cpp_process}. For the Time service is very simple, only the function process needs to be implemented. It gets the incoming and the outgoing message as references and returns a class representing the status the service achieved. 
\lstsetCPP
\lstinputlisting
	[
	label=lst:time_arched_cpp,
	caption={[C++ implementation of the time service. Filename: timeservice.cpp]
	\textbf{C++ implementation of the time service. Filename: timeservice.cpp}}
	]
{../src/services/timeservice/timeservice.cpp}
The service first determines the current time and than creates a SOAP message using the object \textit{PayloadSOAP} on line~\ref{lst_code:time_cpp_process_payloadSOAP}. The class \textit{PayloadSOAP} is able to create a XML message which is conform to the SOAP protocol (The apperance of the generated request and response will be discussed later). I case of the presented time service the payload consists out of two elements nested into one another. The element \textit{text} holds the element child which again holds the string containing the current time.
Within the line~\ref{lst_code:time_cpp_process_message_payload} the payload is passed to the message. 
The message processing is now completed and the function returns its success status on line~\ref{lst_code:time_cpp_return}.
The source code has to be compiled to a dynamic library named \textit{libtimeservice.so}.\\

After the service has been implemented and compiled, it needs to be loaded into the HED. A suitable HED configuration file is to be seen in Listing~\ref{lst:time_arched_xml}. 
\lstsetARCHEDXML
\begin{program}
\lstinputlisting
	[
	label=lst:time_arched_xml,
	caption={[HED configuration for the time service. Filename: arched\_timeservice.xml]
	\textbf{HED configuration for the time service. Filename: arched\_timeservice.xml}}
	]
{../src/services/timeservice/arched_timeservice.xml}
\end{program}
A new path element has been introduced into the element \textit{ModuleMananger}, line~\ref{lst_code:arched_time_moduleManager}. It assigns the location to the compliled dynamic library. 
On line~\ref{lst_code:arched_time_plugin} the library is explict mentioned to be loaded.
Another important change has been done within the \textit{Plexer} element in line~\ref{lst_code:arched_time_plexer_next}. A rule has been introduced which redirects the request to the Time Web Service, if the path of URL is \textit{time}.\\

To run the service again the arched command shown in~\ref{lst:arched_timeservice_ksh} has to be used.
\lstsetKSH
\begin{program}
\begin{lstlisting}[
label=lst:arched_timeservice_ksh,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ arched -c arched_timeservice.xml && echo Daemon started || echo Daemon start failed
Daemon started
\end{lstlisting}
\end{program}

@@

\task{\#ifdef HAVE\_CONFIG\_H\#include <config.h>\#endif - habe ich entfernt... macht keinen Sinn, da keine weiteren Macros im Source Code enthalten sind... oder?}
In the next step a simple client needs to be implemented whose task is to interprete the returned message of the client.
The client needs to have the same protocol stack as the daemon but in contrast to it, it does not need the ability to be loaded as a plugin. As one will see, the creation of this protocol stack on client side is very simple.
The source code of the client consists primarily of the main function and is to be seen in Listing~\ref{lst:time_client_cpp}.
In line~\ref{lst_code:time_client_cpp_logger} the logger is initialized and redirected to the standard error stream.
For the components of the protocol stack are likewise loaded dynamically, one need to specify the installation directory in line~\ref{lst_code:time_client_cpp_init} too.
\task{remark in \textbf{introduction}, what the plexer is for. In our case: to have several services running on one port!!!!!!!!}
The URL of the service is defined in line~\ref{lst_code:time_client_cpp_url}. It fits to the HED configuration file which was shown in Listing~\ref{lst:time_arched_xml}. The daemon is listing on port 60000 and is running on the localhost. The service itself uses HTTP and can be reached by using the path \textit{time}.
Line~\ref{lst_code:time_client_cpp_config} loads the standard config file which is usually almost empty. As a result, no additional security procedures will later be linked into the client sided stack. The protocol stack is created in line~\ref{lst_code:time_client_cpp_client}. Thanks to the URL the information for the configuration can be completed.
The constructor of the class \textit{ClientSOAP} creates a SOAP client which uses HTTP, addresses the port 60000 on localhost. If i.e. HTTPS would have been used, the stack would have been extended by a TLS layer.
Now the client stack is ready, one can create a request to the service. In line~\ref{lst_code:time_client_cpp_message_reqeust} a message which corresponds to the Listing~\ref{lst:time_client_request} is created. The message gets processed by the command in line~\ref{lst_code:time_client_cpp_message_response}. If everything was fine, the message will finally be send to the standard out in line~\ref{lst_code:time_client_cpp_message_answer}.

@@

@@

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:time_client_request,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:time="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:time_client_response,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeResponse>Wed Feb 18 11:20:30 2009</timeResponse>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

>>>>

The first implementation of a Web Service will be a simple time service. 
In case that the service receives a request of a client, it will respond with a string containing the system time.
For simplicity the service will not parse the request but always return the current time.
In the following subsections the implementation of the service and the client will be presented.

@@

In Arc the services are implementated as plugins such that they can easily be included or excluded by modifiying the HED configuration file as it was to be seen in Listing~\ref{lst:arched_arcecho_xml}.
Listing~\ref{lst:time_arched_cpp} contains the C++ implementation of the time service plugin.
The proper class definition of the object \textit{TimeService} is defined in the corresponding header file which is not shown here. It inherits from an object called \textit{Service} defined in the Arc library.
The key element for each plugin is the struct \textit{PluginDescriptor} named \textit{PLUGINS\_TABLE\_NAME} to be seen in line~\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin.
Within the struct a unique plugin name, the type of the plugin, its version and a pointer to a function which returns the instance of the time service has to be defined.
The function which returns the pointer of the instance is desclared in line~\ref{lst_code:time_cpp_get_service}. 
The interface demands an object \textit{PluginArgument} as a parameter but because we are writing a plugin which inherits from \textit{Service}, we are able to expect the \textit{PluginArgument} to be a \textit{ServicePluginArgument}.
%	In the first line of the service the object is downcasted with the operator dynamic_cast
The \textit{ServicePluginArgument} provides access to the HED configuration and the message chain of the service.
%       operator Config* (void) { return config_; };
%       operator ChainContext*   			an interface to manipulate chains stored in Loader
%
%
%
%
The time service uses the namespace \textit{ArcService}. The constructor can be found in line~\ref{lst_code:time_cpp_constructor} and the deconstructor in line~\ref{lst_code:time_cpp_deconstructor}.%
\lstsetCPP%
\lstinputlisting[
	label=lst:time_arched_cpp,
	caption={[C++ implementation of the time service. Filename: timeservice.cpp]
	\textbf{C++ implementation of the time service. Filename: timeservice.cpp}}
	]%
{../src/services/timeservice/timeservice.cpp}%
In the context of the simple service they don't contribute with any functionality.
The method \textit{process} which is required by the inherited class \textit{Service} is defined in line~\ref{lst_code:time_cpp_process} and realises the desired service. 
The parameters \textit{inmsg} and \textit{outmsg} are references to the incoming and outgoing messages. Furthermore the method \textit{process} returns the object \textit{MCCStatus} which is representing the result of the service achieved. 
Within the method \textit{process}, the service first determines the current time and than creates a SOAP payload using the object \textit{PayloadSOAP} on line~\ref{lst_code:time_cpp_process_payloadSOAP}. 
The object \textit{PayloadSOAP} provides enough functionality to create a XML message which is conform to the SOAP protocol 
(The apperance of the generated request and response will be discussed later on page~\pageref{lst:time_client_request}). 
%
%
In the current case the payload consists of two elements nested into one another. The element \textit{time} holds the element \textit{timeResponse} which again holds the string containing the current time.
Within the line~\ref{lst_code:time_cpp_process_message_payload} the payload is stored in the message. 
In case nothing unexpected happened during the message is processed, the function returns with an \textit{MCCStatus} set to \textit{OK} as to be seen in line~\ref{lst_code:time_cpp_return}.\\

%The service has to be compiled into a dynamic library named \textit{libtimeservice.so}, in order
%To run the service, one has to compile the source code into a dynamic library named \textit{libtimeservice.so}.\\
%After the service is shipped into the library \textit{libtimeservice.so} it needs to be copied into the directory \textit{/tmp/arc/tutorial/lib} so it can be found by the \textit{ModuleManager} of the HED.

In order to run the service, it has to be compiled into a dynamic library named \textit{libtimeservice.so}.
The library has be to be copied into the directory \textit{/tmp/arc/tutorial/lib} such that it can be found by the \textit{ModuleManager} of the HED.
A suitable HED configuration file which engages the time service is to be seen in Listing~\ref{lst:time_arched_xml}.A new path element has been introduced into the element \textit{ModuleMananger} in line~\ref{lst_code:arched_time_moduleManager}. It assigns the location of the created dynamic library.
On line~\ref{lst_code:arched_time_plugin} the library is explict mentioned to be loaded as a plugin.
Another important change has been done within the \textit{Plexer} element in line~\ref{lst_code:arched_time_plexer_next}. A rule has been introduced which redirects the request to the time service, if the path of URL is \textit{time}.\\ 
\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:time_arched_xml,float=htb,
	caption={[HED configuration for the time service. Filename: arched\_timeservice.xml]
	\textbf{HED configuration for the time service. Filename: arched\_timeservice.xml}}
	]
{../src/services/timeservice/arched_timeservice.xml}

To start the service the \textit{arched} command which is shown in Listing~\ref{lst:arched_timeservice_ksh} has to be used.
It is recommended to examine the log file \textit{/var/log/arched.log} if the HED configuration file has been modified in order to  assert the start was successful
%To check the start of the HED it is recommended to examine the log file \textit{/var/log/arched.log}.\\
\lstsetKSH
\begin{lstlisting}[
label=lst:arched_timeservice_ksh,float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ arched -c arched_timeservice.xml && echo Daemon started || echo Daemon start failed
Daemon started
\end{lstlisting}

@@

%\task{\#ifdef HAVE\_CONFIG\_H\#include <config.h>\#endif - habe ich entfernt... macht keinen Sinn, da keine weiteren Macros im Source Code enthalten sind... oder?}
In the next step a simple client needs to be implemented whose task is to interprete the returned message of the client.
The client needs to have the same protocol stack as the daemon but in contrast to it, it does not need the ability to be loaded as a plugin. As one will see, the creation of this protocol stack on client side is very simple.
The source code of the client consists primarily of the main function and is to be seen in Listing~\ref{lst:time_client_cpp}.
In line~\ref{lst_code:time_client_cpp_logger} the logger is initialized and redirected to the standard error stream.
For the components of the protocol stack are likewise loaded dynamically, one need to specify the installation directory in line~\ref{lst_code:time_client_cpp_init} too.
\task{remark in \textbf{introduction}, what the plexer is for. In our case: to have several services running on one port!!!!!!!!}
The URL of the service is defined in line~\ref{lst_code:time_client_cpp_url}. It fits to the HED configuration file which was shown in Listing~\ref{lst:time_arched_xml}. The daemon is listing on port 60000 and is running on the localhost. The service itself uses HTTP and can be reached by using the path \textit{time}.
Line~\ref{lst_code:time_client_cpp_config} loads the standard config file which is usually almost empty. As a result, no additional security procedures will later be linked into the client sided stack. The protocol stack is created in line~\ref{lst_code:time_client_cpp_client}. Thanks to the URL the information for the configuration can be completed.
The constructor of the class \textit{ClientSOAP} creates a SOAP client which uses HTTP, addresses the port 60000 on localhost. If i.e. HTTPS would have been used, the stack would have been extended by a TLS layer.
Now the client stack is ready, one can create a request to the service. In line~\ref{lst_code:time_client_cpp_message_reqeust} a message which corresponds to the Listing~\ref{lst:time_client_request} is created. The message gets processed by the command in line~\ref{lst_code:time_client_cpp_message_response}. If everything was fine, the message will finally be send to the standard out in line~\ref{lst_code:time_client_cpp_message_answer}.

@@

Once the HED is running, the service can

@@

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:time_client_request,float,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:time="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:time_client_response,float,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeResponse>Wed Feb 18 11:20:30 2009</timeResponse>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
